Sparse Representation Approaches for First Stage Retrieval: A Review

### 2021-12-03 src/article.tex
Add bibliography about embeddings

    Significant results in natural language processing have been achieved through
    the use of embeddings, numerical representations of words or other linguistic entities.
    At the ranking stage, dense embeddings are successfully applied;
    neural networks are used to form them.
    But this approach is computationally ineffective due to the large number of documents that
    need to be worked with at the first stage.
    Therefore, many researchers pay their attention to sparse embeddings.

>>>>

    Significant results in natural language processing have been achieved through
    the use of embeddings \cite{embedding1, embedding2, embedding3}, numerical representations of
    words or other linguistic entities.
    At the ranking stage, dense embeddings are successfully applied;
    neural networks are used to form them.
    But this approach is computationally ineffective due to the large number of documents that
    need to be worked with at the first stage.
    Therefore, many researchers pay their attention to sparse embeddings.
